MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-21 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
fix markdown output

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn21435176';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of GRCh38 feature counts with CQN normalisation (ACC and DLPFC)';

@@

# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = base_formula, 
                         data = COVARIATES,
                         variables = array(c("(1|Institution)", "(1|Reported_Gender)", "PMI", 
                                                             "ageOfDeath", "RIN", "RIN2", "EV.1", 
                                                             "EV.2", "EV.3", "EV.4", "EV.5")))
phase1
```
Clinical and technical variables selected in phase I are `r paste(adjust.covars, collapse = ', ')`

#### Phase II (batch effects)
```{r phase2}
# Fit a base model with the following covariates
phase2 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = phase1$formula, 
                         data = COVARIATES,
                         variables = array(c("(1|LibraryBatch)", "(1|FlowcellBatch)")))
phase2
```
Clinical, technical and batch variables selected after phase I and II of model identification are `r paste(adjust.covars, collapse = ', ')`

>>>>

```{r synapse.parameters, include=FALSE, cache=FALSE}
parentId = 'syn21435176';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of GRCh38 feature counts with CQN normalisation (ACC and DLPFC)';

@@

# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = base_formula, 
                         data = COVARIATES,
                         variables = array(c("(1|Institution)", "(1|Reported_Gender)", "scale(PMI)", 
                                                             "scale(ageOfDeath)", "scale(RIN)", "scale(RIN2)", "scale(EV.1)", 
                                                             "scale(EV.2)", "scale(EV.3)", "scale(EV.4)", "scale(EV.5)")))
phase1
```

#### Phase II (batch effects)
```{r phase2}
# Fit a base model with the following covariates
phase2 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = phase1$formula, 
                         data = COVARIATES,
                         variables = array(c("(1|LibraryBatch)", "(1|FlowcellBatch)")))
phase2
```
